\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{letterpaper, margin=1in}
\usepackage{parskip} % Adds nice spacing between paragraphs

\begin{document}

% --- Header ---
\begin{center}
    {\Huge \textbf{Syed Rayyan Adil}} \\ \vspace{5pt}
    syed.rayyanadil@gmail.com $|$ +49 152 06835173 \\
    LinkedIn $|$ GitHub
\end{center}

\vspace{20pt}

% --- Date & Salutation ---
\today

\vspace{10pt}

Dear Hiring Manager,

\vspace{10pt}

% --- Body ---
As a strong believer in the transformative power of mobility, I am drawn to this backend role at a company that is revolutionizing the way people move.

My experience in delivering reliable backend solutions has equipped me with the skills to make an immediate impact. At Schwarz Digits, I successfully implemented Azure DevOps CI/CD pipelines and PostgreSQL schema migrations with Liquibase, ensuring repeatable Docker and Kubernetes deployments. Additionally, my work at GoodCore Software involved refactoring state management with Redux and integrating Zoom API for client meetings, resulting in enhanced system stability. I also built and shipped production-ready React features end-to-end, collaborating with Product Managers via Jira.

As an MSc AI student, I am well-versed in the technical aspects of software development. Although I don't have direct experience with AI in a professional setting, my thesis work has given me a solid foundation in computer vision and machine learning. However, I believe my strengths lie in backend development, where I have gained significant experience in designing and implementing scalable architectures. My experience with REST APIs, SQL, and Git will enable me to make a seamless transition into this role.

With a strong foundation in Python, Docker, and backend development, I am confident in my ability to drive technical innovation and excellence. I look forward to discussing how my skills and experience align with the needs of the company, and I am eager to explore how I can contribute to the team's success.



\vspace{20pt}

% --- Sign-off ---
Sincerely, \\
\vspace{10pt}
\textbf{Syed Rayyan Adil}

\end{document}